Cloudbreak: A MapReduce Algorithm for Detecting Genomic Structural Variation

### 2013-04-05 manuscript/chr2DeletionPredsFDR10.table.brew.tex
update chr2 max sensitivity table to have precision, recall
Separate delly calls into two sets

\begin{table}[t]
\begin{center}
\begin{tabular}{rrrrrr}
  \hline
 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number & <%= totals['40-100bp'] %> &  <%= totals['101-250bp'] %> & <%= totals['251-500bp'] %> &  <%= totals['501-1000bp'] %> & <%= totals['> 1000bp'] %>\\ 
  \hline
  Cloudbreak  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '> 1000bp') %> \\ 
  Breakdancer & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '> 1000bp') %> \\ 
  GASVPro     & <%= printPredTableCell(preds, exPreds, 'GASVPro', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'GASVPro', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'GASVPro', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '> 1000bp') %> \\ 
  DELLY       & <%= printPredTableCell(preds, exPreds, 'DELLY', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY', '> 1000bp') %> \\ 
  Pindel      & <%= printPredTableCell(preds, exPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '> 1000bp') %>\\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter indels found by each tool at a 10\% FDR, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2DeletionPreds}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\begin{tabular}{rrrrrr}
  \hline
 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number & <%= totals['40-100bp'] %> &  <%= totals['101-250bp'] %> & <%= totals['251-500bp'] %> &  <%= totals['501-1000bp'] %> & <%= totals['> 1000bp'] %>\\ 
  \hline
  Cloudbreak  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '> 1000bp') %> \\ 
  Breakdancer & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '> 1000bp') %> \\ 
  GASVPro     & <%= printPredTableCell(preds, exPreds, 'GASVPro', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'GASVPro', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'GASVPro', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '> 1000bp') %> \\ 
  DELLY-RP       & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '> 1000bp') %> \\ 
  DELLY-SR       & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '> 1000bp') %> \\ 
  Pindel      & <%= printPredTableCell(preds, exPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '> 1000bp') %>\\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter indels found by each tool at a 10\% FDR, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2DeletionPredsFDR10}
\end{table}

### 2013-04-05 manuscript/chr2DeletionPredsMaxSensitivity.table.brew.tex
Separate delly calls into two sets

\begin{table}[t]
\begin{center}
\begin{tabular}{rrrrrr}
  \hline
 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number & <%= totals['40-100bp'] %> &  <%= totals['101-250bp'] %> & <%= totals['251-500bp'] %> &  <%= totals['501-1000bp'] %> & <%= totals['> 1000bp'] %>\\ 
  \hline
  Cloudbreak  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '> 1000bp') %> \\ 
  Breakdancer & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '> 1000bp') %> \\ 
  GASVPro     & <%= printPredTableCell(preds, exPreds, 'GASVPro', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'GASVPro', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'GASVPro', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '> 1000bp') %> \\ 
  DELLY       & <%= printPredTableCell(preds, exPreds, 'DELLY', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY', '> 1000bp') %> \\ 
  Pindel      & <%= printPredTableCell(preds, exPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '> 1000bp') %>\\ 
  MoDIL      & <%= printPredTableCell(preds, exPreds, 'MoDIL', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'MoDIL', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'MoDIL', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'MoDIL', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'MoDIL', '> 1000bp') %>\\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter indels found by each tool at a 10\% FDR, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2DeletionPreds}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\begin{tabular}{rrr|rrrrr}
  \hline
                        & Prec. & Recall & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
 Total Number &          &           & <%= totals['40-100bp'] %> &  <%= totals['101-250bp'] %> & <%= totals['251-500bp'] %> &  <%= totals['501-1000bp'] %> & <%= totals['> 1000bp'] %>\\ 
  \hline
  Cloudbreak    &  <%= printPredTableValueFromList('Cloudbreak', precision) %> & <%= printPredTableValueFromList('Cloudbreak', recall) %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Cloudbreak', '> 1000bp') %> \\ 
  Breakdancer   &  <%= printPredTableValueFromList('Breakdancer', precision) %> & <%= printPredTableValueFromList('Breakdancer', recall) %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Breakdancer', '> 1000bp') %> \\ 
  GASVPro        & <%= printPredTableValueFromList('GASVPro', precision) %> & <%= printPredTableValueFromList('GASVPro', recall) %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'GASVPro', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'GASVPro', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'GASVPro', '> 1000bp') %> \\ 
  DELLY-RP           & <%= printPredTableValueFromList('DELLY', precision) %> & <%= printPredTableValueFromList('DELLY', recall) %> & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-RP', '> 1000bp') %> \\ 
  DELLY-SR           & <%= printPredTableValueFromList('DELLYSR', precision) %> & <%= printPredTableValueFromList('DELLYSR', recall) %> & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'DELLY-SR', '> 1000bp') %> \\ 
  Pindel           & <%= printPredTableValueFromList('Pindel', precision) %> & <%= printPredTableValueFromList('Pindel', recall) %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'Pindel', '> 1000bp') %>\\ 
  MoDIL           & <%= printPredTableValueFromList('MoDIL', precision) %>  & <%= printPredTableValueFromList('MoDIL', recall) %> & <%= printPredTableCell(preds, exPreds, 'MoDIL', '40-100bp') %>  & <%= printPredTableCell(preds, exPreds, 'MoDIL', '101-250bp') %> &  <%= printPredTableCell(preds, exPreds, 'MoDIL', '251-500bp') %> & <%= printPredTableCell(preds, exPreds, 'MoDIL', '501-1000bp') %> & <%= printPredTableCell(preds, exPreds, 'MoDIL', '> 1000bp') %>\\ 
   \hline
\end{tabular}
\end{center}
\caption{The number of simulated deletions in the 30X diploid chromosome 2 with Venter indels found by each tool at maximum sensitivy, as well as the number of those deletions that were discovered exclusively by each tool (in parentheses). The total number of deletions in each size class in the true set of deletions is shown in the second row of the header.}
\label{chr2DeletionPredsMaxSensitivity}
\end{table}

### 2013-04-05 manuscript/manuscript.tex
Separate delly calls into two sets

\begin{table}
\begin{center}
\begin{tabular}{r|r|rrr|rrr}
\multicolumn{2}{c}{}  & \multicolumn{3}{c}{Simulated Data} & \multicolumn{3}{c}{NA18507} \\
\hline
 & SV Types &  Single CPU & Parallel & Proc. &  Single CPU & Parallel & Proc.  \\ 
  \hline
  Cloudbreak & D,I &   NA    & 308 & 312    & NA         & 2,310 & 636 \\ 
  Breakdancer & D,I,V,T &  653   & NA       & NA          & 134,170 &  5,586 & 84 \\
  GASVPro & D,V   &  3,339  & NA       & NA         & 52,385  & NA & NA \\
  DELLY & D         &  1,964 & NA          & NA      & 14,475  & 37,390 & 84 \\
  Pindel & D,I,V,P         & 37,006 &  4,885     & 8          &  284,932  & 28,587 & 84 \\ 
  MoDIL & D,I        &  NA      & 52,547 & 250 & NA         & NA  & NA\\ 
   \hline
\end{tabular}
\end{center}
\caption{Runtimes (elapsed) on both data sets of each tool tested, in single-processor and parallel mode. For parallel runs, Proc. is the maximum number of simultaneously running processes or threads. All times are in seconds. The types of variants detected by each program are listed with the abbreviations: D - deletion; I - insertion; V - Inversion; P - duplication; T - translocation. Interchromosomal translocations are only detected by Breakdancer in single CPU mode. }
\label{runtimes}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{r|r|rrr|rrr}
\multicolumn{2}{c}{}  & \multicolumn{3}{c}{Simulated Data} & \multicolumn{3}{c}{NA18507} \\
\hline
 & SV Types &  Single CPU & Parallel & Proc. &  Single CPU & Parallel & Proc.  \\ 
  \hline
  Cloudbreak & D,I &   NA    & 308 & 312    & NA         & 2,310 & 636 \\ 
  Breakdancer & D,I,V,T &  653   & NA       & NA          & 134,170 &  5,586 & 84 \\
  GASVPro & D,V   &  3,339  & NA       & NA         & 52,385  & NA & NA \\
  DELLY & D         &  1,964 & NA          & NA      & 30,311  & 20,224 & 84 \\
  Pindel & D,I,V,P         & 37,006 &  4,885     & 8          &  284,932  & 28,587 & 84 \\ 
  MoDIL & D,I        &  NA      & 52,547 & 250 & NA         & NA  & NA\\ 
   \hline
\end{tabular}
\end{center}
\caption{Runtimes (elapsed) on both data sets of each tool tested, in single-processor and parallel mode. For parallel runs, Proc. is the maximum number of simultaneously running processes or threads. All times are in seconds. The types of variants detected by each program are listed with the abbreviations: D - deletion; I - insertion; V - Inversion; P - duplication; T - translocation. Interchromosomal translocations are only detected by Breakdancer in single CPU mode. }
\label{runtimes}
\end{table}
